Project Contract\\Local Adaptive Optimization of Timestep

### 2013-09-03 report/report.tex
Added more compiler-files to gitignore (latex) and updated project contract

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}

@@

\title{Local Adaptive Optimization of Timestep}
\author{Malte Stær Nissen\\University of Copenhagen\\\texttt{malte.nissen@gmail.com}}

@@

Supervisor: Sune Darkner\\\texttt{darkner@diku.dk}

\section{Problem}

\subsection{Why?}
In order to minimize the risk of grids exploding/imploding caused by too large timesteps and avoid the need to compute the smaller timesteps on the entire grid.

\subsection{How?}

\subsection{Learning goals}
Evaluate local adaptive optimization of timesteps to minimize the risk of unwanted deformations in grids.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

@@

\title{Project Contract\\Local Adaptive Optimization of Timestep}
\author{Malte Stær Nissen\\University of Copenhagen\\\texttt{malte.nissen@gmail.com}\\Supervisor: Sune Darkner\\\texttt{darkner@diku.dk}}

@@

\section{Learning Goals}
Course specific learning goals:
\begin{enumerate}
	\item Formulate an operational project plan.
	\item Search the relevant literature and write a literature review setting own work in perspective.
	\item Be able to formulate what plagiarism is, and demonstrate proper citation and reference style.
	\item Solve a selected problem of fair Computational and Mathematical Modelling / eScience content and difficulty.
	\item Produce a thorough experiment plan that clearly demonstrates the quality of and highlights boundaries for the solution. 
	\item Produce a scientific text of fair quality both textually and scientifically.
	\item The student must be able to make an oral presentation of own work.
\end{enumerate}
Project specific learning goals:
\begin{enumerate}
	\item Evaluate local adaptive optimization of timesteps to minimize the risk of unwanted deformations in grids.
\end{enumerate}

\section{Problem Description}

\subsection{Problem Statement}

\subsection{Motivation}

\subsection{Proposed solution}

\subsection{Success criteria}
